%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing


\begin{document}

\header{Jacob}{Stuart}{Software Engineering Intern} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
14003 Waterford Ln
San Diego, CA 92129
USA
~
(858) 602 2088
~
\href{mailto:stuart4@purdue.edu}{Stuart4@Purdue.edu}
\href{http://stuartresearch.org}{StuartResearch.org}
\href{https://www.github.com/Stuart4}{Github://Stuart4}
~
\section{Technical Skills}
Java, C/C++,
Android Development,
Linux Kernel,
Git Source Control,
Node.js
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--Now}
{Bachelor of Science {\normalfont Computer Science} (3.6)}
{Purdue University}
{Expected May 2017\\
Software Engineering and Computer Security Concentration\\
Management Minor}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}

%------------------------------------------------

\entry
{May 2015}
{Radio 91x}
{Android Application}
{An Android application designed to stream music in the background with a modern and intuitive material design interface, song history, and favorites.
\begin{itemize}
\item Foreground Service with IBinder Communication
\item Material Design
\item Sqlite Backend
\end{itemize}}

%------------------------------------------------

\entry
{May 2015}
{The Crate Escape}
{Unity Game}
{2D infinite runner with raycasting, an object pool, and advanced vector-based movement.
\begin{itemize}
\item Xbox 360 Controller Support
\item Unique Graphics
\end{itemize}}

%------------------------------------------------

\entry
{Dec 2014}
{Purdue Eats}
{Android Application}
{Website crawler that parses the Purdue Dining Court's menus to provide a native interface.
\begin{itemize}
\item Rock Solid Stability
\item Favorites, Dislikes, Intelligent Anticipation
\item Sqlite Backend
\end{itemize}}

%------------------------------------------------

\entry
{June 2015}
{Push Torrent}
{Node.js Server Applicaton}
{Nonblocking server application to follow a websocket and intelligently download links.
\begin{itemize}
\item Websockets
\item Gzip Support
\end{itemize}}

%------------------------------------------------

\entry
{April 2015}
{IRC Client}
{C++ with GTK GUI}
{Server and client reimplementation of the IRC specification.
\begin{itemize}
\item GTK Gui
\item Featureful C Networking
\end{itemize}}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}

\entry
{2015--Now}
{Linux Kernel Development}
{Kernel C}
{I am Currently taking the Eudyptula Challenge. So far, my drivers work includes a simple USB driver and misc char device driver.}

\end{entrylist}

\section{Awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--Now}
{Dean's List}
{Purdue University}
{Awarded to the top students academically.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Relevent Coursework}

\begin{entrylist}

%------------------------------------------------

\entry
{Fall 2014}
{Introduction to Object Oriented Programming}
{Purdue University}

%------------------------------------------------

\entry
{Spring 2015}
{Programming in C}
{Purdue University}

%------------------------------------------------

\entry
{Spring 2015}
{Foundations of Computer Science}
{Purdue University}

%------------------------------------------------

\entry
{Spring 2015}
{Scientific Writing and Presenting}
{Purdue University}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{professional:} mobile application development, economics, UX design, software design

\textbf{personal:} longboarding, cars, movies

\end{document}
